The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-10-25 manuscript/manuscript.tex
Update for resubmit (bold version)

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. \ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $\sim7$ which} persists even after accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar). The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}. Currently, the physical mechanism that can produce such a tight relationship is unknown due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations, possibly by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}, not necessarily in a direct manner.
On the other hand, there may not be a need for a physical coupling \citep{Peng2007, Jahnke2011, Hirschmann2010}, the statistical convergence from galaxy assembly alone (i.e., mergers) may reproduce the observed correlations.

To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}. During the past decade, there has been much progress on this front using type-1 AGNs. For example, it has been demonstrated at $z<1$ that at fixed \mbh\ the host galaxies are under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}. Similarly, \citet{Bennert11} and \citet{Woo++08} found a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component. At $z>1$, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies. Although, the accuracy of such an approach for luminous AGNs has not yet been well established as discussed herein. If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.  A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011} through bar instabilities or minor mergers.

@@

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}. {\bf Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample. We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues~\ref{sec:compare_sample}.}

@@

\section{Experimental design}
\label{sec:data}
We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data. Specifically, we focused on meeting the following criteria to overcome the limitations of previous studies:

@@

\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.

\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, which is below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.

@@

\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.}. %The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.

@@

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling provided by this work are performed through a common procedure for spectral model fits. This approach first corrects the spectra for galactic extinction and shifts them to the rest-frame. The spectral regions in the near-IR that are strongly affected by OH emission are masked. The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on $\chi^2$ minimization. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$. The bolometric luminosities are measured from the broad AGN lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. The flux-limited nature of the sample results in a slightly higher Eddington ratio distribution at lower \mbh\, as shown in Figure~\ref{fig:selection}. Moreover, we have a higher preference to select targets which have rest-frame UV images (i.e., \hst/ACS) as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field. We list the 32 AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.

@@

Note that these recipes are first provided by \citet{Vestergaard2006}. Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs. While fourteen AGNs have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample. It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, UltraVISTA in the case of COSMOS, thus amounting to an effective aperture correction. While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence lower signal-to-noise. We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. {\bf Note that the B10 only provides the galaxy single V-band luminosity. \citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf . Similarly to B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from the V-band based on the same stellar template. Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

@@

%Introduce Lenstronomy:
We use the image modeling tool \lenstronomy~\citep{Birrer2015, lenstronomy} to perform the decomposition of the host and nuclear light. \lenstronomy\ is a multi-purpose open-source gravitational lens image forward-modeling package written in Python. 
Its flexibility enables us to turn off the lensing channel and focus on the AGN and host decomposition\footnote{As a check, we compared the results from \lenstronomy\ to the commonly used galaxy modeling software {\sc Galfit} and confirmed that the results are consistent between the two.}. The main advantage of \lenstronomy\ is that it returns the full posterior distribution of each parameter (i.e., not just the best fit model) and the Laplace approximation of the uncertainties. The input ingredients to \lenstronomy\ include:
\begin{enumerate}
\item AGN imaging data. \\
-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as  a compromise between capture all the flux and keeping the background noise low and the computational time short. We found that extending the radius beyond $1\farcs5$ did not add any missing light, while it increased the noise and computational time. %By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.
}. By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$). If needed, a larger box size {\bf is selected to} include nearby objects. 
\item Noise level map.\\
-- The origin of the noise in each pixel stems from the read noise, background noise, and Poisson noise from the astronomical sources themselves. We measure these directly from the empty regions of the data. We then calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. A final noise map includes all of these sources of error.

@@

We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts. We measure the effective radius (\Reff), \sersic\ index, and host-to-total flux ratio and describe each of these in the following section. We recognize that these measurements are weighted by the eight top-ranked PSFs. The limited number of top-ranked PSFs may underestimate actual uncertainties. To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are consistent. For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector. This finding underscores that position on the detector is not the main factor driving the PSF shape. Other factors that are likely to be more significant are sub-pixel centering, intrinsic color of the star, and jitter and thermal status of the telescope during the observations. The complexity of the problem}
highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.

@@

From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}. \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases. While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample. This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass. In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.

@@

The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}. Based on the redshift, we calculate the physical scale radius of each object in kpc assuming a standard cosmology. We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). 
{\bf Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels. In order to check whether this affects our conclusions,  we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$). In particular, the}
inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistency of the re-fitting results and} the small scatter in the host flux ($<10\%$).

@@

For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.  We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}). {\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}. We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.

>>>>

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., {\bf total} stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we {\bf acquired} {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images {\bf including available ACS data}, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find {\bf that} the {\it observed} ratio {\bf of \mbh\ to total \smass\ is $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. {\bf A non-evolving mass ratio is consistent with the data at the 2-3$\sigma$ confidence level when accounting for selection effects (estimated using two independent and complementary methods), and their uncertainties.} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results {\bf cannot distinguish whether SMBHs and their total host stellar mass and luminosity proceed in lockstep or whether the growth of the former somewhat overshoots the latter, given the uncertainties. Based on a statistical estimate} of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is {\bf offset from the local value by a factor of $\sim7$ which} is significant even accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to {\bf correlate} with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar). The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}. Currently, the physical mechanism that can produce such a tight relationship is unknown due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations, possibly by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}, not necessarily in a direct manner.
On the other hand, there may not be a need for a physical coupling \citep{Peng2007, Jahnke2011, Hirschmann2010}, the statistical convergence from galaxy assembly alone (i.e., mergers) may reproduce the observed correlations.

To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they {\bf emerge and evolve} over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}. During the past decade, there has been much progress on this front using type-1 AGNs. For example, it has been demonstrated that {\bf AGN host galaxies, at $z<1$ and for fixed \mbh, are} under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}. Similarly, \citet{Bennert11} and \citet{Woo++08} found a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component. At $z>1$, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies. Although, the accuracy of such an approach for luminous AGNs has not yet been well established as discussed herein. If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.  A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the {\bf bulge \citep{Jah++09,Bennert++2011,SS13} through} bar instabilities or minor mergers.

@@

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies {\bf with} a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}. {\bf Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample. We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues (Section~\ref{sec:compare_sample}).}

@@

\section{Experimental design}
\label{sec:data}
We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass {\bf measurements} and fall within deep extragalactic survey fields that offer rich ancillary data. Specifically, we focused on meeting the following criteria to overcome the limitations of previous studies:

@@

\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which {\bf avoid} potential systematic uncertainties in UV-based estimators \citep{Greene2005}.

\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, are below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.

@@

\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.} %The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.

@@

The 32 AGNs are initially selected by the X-ray observations {\bf of COSMOS}~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling provided by this work are performed through a common procedure for spectral model fits. This approach first corrects the spectra for galactic extinction and shifts them to the rest-frame. The spectral regions in the near-IR that are strongly affected by OH emission are masked. The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on $\chi^2$ minimization. We refer the reader to the aforementioned paper for further details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

{\bf Based on the \mbh\ estimates} described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$. The bolometric luminosities are measured from the broad AGN lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. The flux-limited nature of the sample results in a slightly higher Eddington ratio distribution at lower \mbh\, as shown in Figure~\ref{fig:selection}. Moreover, we have a higher preference to select targets which have rest-frame UV images (i.e., \hst/ACS) as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field. We list the 32 AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.

@@

Note that these recipes are first provided by \citet{Vestergaard2006}. Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs. While fourteen AGNs have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample. While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence lower signal-to-noise. We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.

{\bf It is worth noting that the absolute flux calibration of the FMOS spectra is set to match the available ground-based IR imaging, UltraVISTA in the case of COSMOS. While an initial flux calibration is performed during the reduction of the FMOS data using calibration stars, there can be differential flux loss due to aperture effects, variable seeing conditions, and minor alignment issues with the instrument. The flux normalization is effectively an aperture correction in the J or H band depending on the source redshift. We note that this procedure does not correct for intrinsic variability that may induce an additional error of 0.2 mag. We refer the reader to Section 2.2 of \citet{Schulze2018} for full details on the flux calibration.}

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. {\bf Note that B10 only provides the single galaxy V-band luminosity. \citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using a single band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. {\bf Similar to the B10 sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-corrections from the V-band based on the same stellar template. Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

@@

%Introduce Lenstronomy:
We use the image modeling tool \lenstronomy~\citep{Birrer2015, lenstronomy} to perform the decomposition of the host and nuclear light. \lenstronomy\ is a multi-purpose open-source gravitational lens image forward-modeling package written in Python. 
Its flexibility enables us to turn off the lensing channel and focus on the AGN and host decomposition\footnote{As a check, we compared the results from \lenstronomy\ to the commonly used galaxy modeling software {\sc Galfit} and confirmed that the results are consistent between the two.}. The main advantage of \lenstronomy\ is that it returns the full posterior distribution of each parameter (i.e., not just the best fit model) and the Laplace approximation of the uncertainties. The input ingredients to \lenstronomy\ include:
\begin{enumerate}
\item AGN imaging data. \\
-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as a compromise between the detection of the total flux and a minimization of the background noise while keeping the computational time low. We found that extending the radius beyond $1\farcs5$ did not add any missing light, while it increased the noise and computational time. %By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.
}. By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$). If needed, a larger box size {\bf is selected to} include nearby objects. 
\item Noise level map.\\
-- The origin of the noise in each pixel stems from the read noise, background noise, and Poisson noise from the astronomical sources themselves. We measure these directly from the empty regions of the data. We then calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. A final noise map includes all of these sources of error.

@@

We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts. We measure the effective radius (\Reff), \sersic\ index, and host-to-total flux ratio and describe each of these in the following section. We recognize that these measurements are weighted by the eight top-ranked PSFs. The limited number of top-ranked PSFs may underestimate actual uncertainties. To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are consistent. For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the {\bf AGN position on the detector. This finding underscores that position on the detector is not the main factor driving the PSF shape. Other factors, likely to be more significant, are the sub-pixel centering, the intrinsic color of the star, and the jitter and thermal status of the telescope during the observations. The complexity of the problem}
highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.

@@

From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has a host-to-total flux ratio lower than $15\%$}. \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases. While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample. This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass. In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.

@@

The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}. Based on the redshift, we calculate the physical scale of the radius for each object in kpc assuming a standard cosmology. We plot them together with measured \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems {\bf have} a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). 
{\bf Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels. In order to check whether this affects our conclusions,  we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$). In particular, the}
inferred \Reff\ for {\bf three} systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistency of the re-fitting results and} the small scatter in the host flux ($<10\%$).

@@

For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.  We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}). {\bf To minimize the uncertainty associated with these corrections, we use these two templates to interpolate to the rest-frame R band which is very close to the observed wavelengths}. We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
